Reproductive Allocation Calculations

### 2015-03-24 leaflifespan.Rmd
Change variable name tag_ID -> individual

# InvestmentSummary <- InvestmentSummary
# names(InvestmentSummary)[1] <- "tag_ID"

@@

# Create new dataset taking only count measures, bc these are ultimately what we want
leaf_lifespan <- raw_leaf_lifespan %>%
  select(species,age,site,tag_ID,d_start,d_end,length_start,new_length,segment,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)

@@

```{r, echo=FALSE,results='hide', message=FALSE}
#adding leaf, stem weight data from InvestmentSummary to raw_leaf_lifespan dataframe; can't RUN LINES 95-108 UNTIL INVESTMENT SUMMARY OPEN - THEN PROBLEM WITH PLYR
#raw_leaf_lifespan <- left_join(raw_leaf_lifespan, InvestmentSummary, by = "tag_ID")

>>>>

# InvestmentSummary <- InvestmentSummary
# names(InvestmentSummary)[1] <- "individual"

@@

# Create new dataset taking only count measures, bc these are ultimately what we want
leaf_lifespan <- raw_leaf_lifespan %>%
  select(species,age,site,individual,d_start,d_end,length_start,new_length,segment,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)

@@

```{r, echo=FALSE,results='hide', message=FALSE}
#adding leaf, stem weight data from InvestmentSummary to raw_leaf_lifespan dataframe; can't RUN LINES 95-108 UNTIL INVESTMENT SUMMARY OPEN - THEN PROBLEM WITH PLYR
#raw_leaf_lifespan <- left_join(raw_leaf_lifespan, InvestmentSummary, by = "individual")
